---
title: "FYP preliminary analyses"
author: "Katie Cheng"
date: "October 8, 2015"
output: 
  ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape)
library(reshape2)

# load functions
source("/Users/Katie/Desktop/Stanford/R/multiplot.R")
source("/Users/Katie/Desktop/Stanford/R/summarySE.R")
```

## Contents

- Histograms of data
- Bar charts comparing group means
- Correlations & scatterplots testing Ease x Utility
- Models for Likelihood, as predicted by Ease & Utility


```{r load_strategy_prompts, include=FALSE}

longStrats = c(
  "Go back and try to figure out something you're confused about in the readings for the class.",
  "Skim new course material to see how it is organized before you study it thoroughly.", 
  "Adjust the way you study in order to fit the course.", 
  "Think through a topic and decide what you are supposed to learn from it before you read it.",
  "Relate ideas you are learning in the course to those in other courses.", 
  "Play around with ideas of your own related to what you are learning in the course.", 
  "Write brief summaries of the main ideas from the readings and the concepts from the lectures.",
  "Set goals for yourself in order to direct your activities in the study period."
)

shortStrats = c(
  "figure_confused",
  "skim_new",
  "adjust_study",
  "decide_learn",
  "relate_courses",
  "play_ideas",
  "summarize_ideas",
  "set_goals"
)

# code strategy dimensions
prepare_act = as.factor(c(1, 0, 0, 0, 1, 1, 1, 0))
open_clearstop = as.factor(c(1, 1, 0, 0, 0, 0, 1, 1))
stratDimensions = data.frame(strategy = c(1:8), 
                             shortStrats,
                             longStrats,
                             prepare_act, 
                             open_clearstop)
stratDimensions$strategy = as.factor(stratDimensions$strategy)
levels(stratDimensions$prepare_act)[1:2] = c("prepare", "act")
levels(stratDimensions$open_clearstop)[1:2] = c("open", "clearstop")
stratDimensions$prepare_act_open_clearstop = paste(stratDimensions$prepare_act, "_", 
                                                   stratDimensions$open_clearstop, sep="")
stratDimensions

```

```{r wrangling, include=FALSE}

# Wrangling raw CSV from Qualtrics

# First, open the CSV and delete the second row (containing descriptive text)
# Why? It messes up the data import

# load data
raw_data = read.csv("/Users/Katie/Desktop/Stanford/1st year project/3_FYP study/version_09-23-15_qualtrics/10-08-15_FYP_Effort_and_Utility_in_SRL2.csv")

# inspect raw data
# dplyr::glimpse(raw_data)

# I don't currently do anything with this
qual_data = dplyr::select(
  raw_data,
  matches("id"),
  matches("ESA1"),
  matches("ESA2"),
  matches("USA1"),
  matches("USA2"),
  matches("C7Time_3"),
  matches("SA1"),
  matches("SA2"),
  matches("^D.")
)

data = dplyr::select(
  raw_data, 
  matches("id"),
  matches("^D."),
  num_range("V", 8:9),
  matches("C3Time_3"),
  matches("ETime_3"),
  matches("UTime_3"),
  matches("LTime_3"),
  matches("C7Time_3"),
  num_range("E", 1:8),
  num_range("U", 1:8),
  num_range("L", 1:8)
)

# Edit survey start & end data:
data = tidyr::separate(data, "V8", c("startDate", "startHour"), sep=" ")
data = tidyr::separate(data, "V9", c("endDate", "endHour"), sep=" ")

# Rename variables
data = dplyr::rename(data, 
                     REP_id = id,
                     timeContext = C3Time_3,
                     timeEase = ETime_3,
                     timeUtility = UTime_3,
                     timeLikelihood = LTime_3,
                     timeShortAns = C7Time_3,
                     age = D1,
                     gender = D2,
                     academicExp = D3,
                     yearMiddle = D3a,
                     yearHigh = D3b,
                     yearCollege = D3c,
                     yearCollegeTxt = D3c_TEXT,
                     yearGrad = D3d,
                     yearGradTxt = D3d_TEXT,
                     taughtStudy = D4
                     )

### fix data ###

# make EUL and taughtStudy into ordinal variables
data = dplyr::mutate_each_(data, dplyr::funs(as.ordered(.)), names(data[-20:-1]))
data$taughtStudy = as.ordered(data$taughtStudy)
levels(data$taughtStudy) = c("strongly\ndisagree", "disagree", "somewhat\ndisagree", 
                             "neither agree\nnor disagree", "somewhat\nagree", 
                             "agree", "strongly\nagree")

# add a pid
data = cbind("pid" = seq.int(nrow(data)), data)

# turn age from string into an integer
data = tidyr::separate(data, age, c("age", "extra"), sep=2)
data$age = as.integer(data$age)
data$extra = NULL

# make an ageCat variable (note: unevenly distributed bins)
data$ageCat = as.factor(findInterval(data$age, c(16, 21, 26)))
levels(data$ageCat)[1:4] = c("11-15", "16-20", "21-25", "26 & up")

# name levels gender
data$gender = as.factor(data$gender)
levels(data$gender)[1:2] = c("male", "female")

## fix the academic years shenanigans ##

# merge yearCollege and yearCollegeTxt
data$yearCollegeMC = data$yearCollege
data$yearCollege = data$yearCollegeTxt
data$yearCollegeTxt = NULL

# merge yearGrad and yearGradTxt
data$yearGradMC = data$yearGrad
data$yearGrad = data$yearGradTxt
data$yearGradTxt = NULL

# privileging text responses over MC responses
for (i in 1:nrow(data)) {
  if (is.na(data$yearCollege[i])) {
    data$yearCollege[i] = data$yearCollegeMC[i]
  } 
  if (is.na(data$yearGrad[i])) {
    data$yearGrad[i] = data$yearGradMC[i]
  }
}

data$yearCollegeMC = NULL
data$yearGradMC = NULL

# merge all years
# +1 for K, +5 for 1:5, +3 for 6:8, +4 for 9:12, +4 for Frosh-Senior
for (i in 1:nrow(data)) {
  if (is.na(data$academicExp[i])) {
    # do nothing
  }
  else if (data$academicExp[i] == 1) {
    # middle school
    data$acadExpYears[i] = 1 + 5 + data$yearMiddle[i]
  } else if (data$academicExp[i] == 2) {
    # high school
    data$acadExpYears[i] = 1 + 5 + 3 + data$yearHigh[i]
  } else if (data$academicExp[i] == 3) {
    # undergrad
    data$acadExpYears[i] = 1 + 5 + 3 + 4 + data$yearCollege[i]
  } else if (data$academicExp[i] == 4) {
    # grad
    data$acadExpYears[i] = 1 + 5 + 3 + 4 + 4 + data$yearGrad[i]
  }
}

data$yearMiddle = NULL
data$yearHigh = NULL
data$yearCollege = NULL
data$yearGrad = NULL

# name academicExp levels
data$academicExp = as.factor(data$academicExp)
levels(data$academicExp)[1:4] = c("middle", "high", "college", "grad")

# melt data into long vector
melt_data = melt(data, id=c(
  "pid", "REP_id", "age", "ageCat", "gender", "academicExp", "acadExpYears", "taughtStudy",
  "startDate", "startHour", "endDate", "endHour", "timeContext", "timeEase", "timeUtility",
  "timeLikelihood", "timeShortAns"))

melt_data = tidyr::separate(melt_data, variable, c("EUL", "strategy"), sep=1)
melt_data$strategy = as.integer(melt_data$strategy)

# fix variable types in melted data
melt_data$taughtStudy = as.ordered(melt_data$taughtStudy)
melt_data$EUL = as.factor(melt_data$EUL)
melt_data$EUL = factor(melt_data$EUL, levels = c("E", "U", "L"))
melt_data$strategy = as.factor(melt_data$strategy)
melt_data$value = as.ordered(melt_data$value)
melt_data = dplyr::rename(melt_data, rating = value)

# add an index
melt_data = cbind("index" = seq.int(nrow(melt_data)), melt_data)

dplyr::glimpse(melt_data)

# remove items where the participant didn't rate E, U, and L on the strategy
to_delete = NULL
for (i in 1:nrow(melt_data)) {
  if (is.na(melt_data$rating[i])) {

    participant_id = melt_data$pid[i]
    incomplete_strategy = melt_data$strategy[i]

    delete_rows = as.vector(dplyr::filter(
      melt_data,
      pid==participant_id & strategy==incomplete_strategy)$index)

    to_delete = c(to_delete, delete_rows)
  }
}

melt_data = melt_data[-unique(to_delete), ]

# redo the index now that rows have been deleted
melt_data$index = seq.int(nrow(melt_data))

# add strategy dimensions
melt_data = dplyr::left_join(melt_data, stratDimensions, by="strategy")

# inspect data
dplyr::glimpse(melt_data)

```


## | "I study the way that I do because a teacher (or teachers) taught me to study that way."

```{r hist_taughtStudy}

dfTaught = data.frame(taughtStudy = na.omit(data$taughtStudy))

ggplot(dfTaught, aes(x = taughtStudy)) +
  geom_histogram(color='black',
                 fill='lightgrey',
                 binwidth=1,
                 breaks=c(0.5:7.5)) +
  theme_bw()

```


## Time on task: Reading context
```{r hist_time_context}

dftimeContext = data.frame(timeContext = na.omit(data$timeContext))

ggplot(dftimeContext, aes(x = dftimeContext$timeContext)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("milliseconds") +
  theme_bw()

```

## Time on task: Doing Ease likert rating & short answers
```{r hist_time_ease}

dftimeEase = data.frame(timeEase = na.omit(data$timeEase))

ggplot(dftimeEase, aes(x = dftimeEase$timeEase/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Time on task: Doing Utility likert rating & short answers
```{r hist_time_utility}

dftimeUtility = data.frame(timeUtility = na.omit(data$timeUtility))

ggplot(dftimeUtility, aes(x = dftimeUtility$timeUtility/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Time on task: Doing Likelihood likert rating
```{r hist_time_likelihood}

dftimeLikelihood = data.frame(timeLikelihood = na.omit(data$timeLikelihood))

ggplot(dftimeLikelihood, aes(x = dftimeLikelihood$timeLikelihood/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Time on task: Doing short answer descriptions of study strategies
```{r hist_time_sa}

dftimeShortAns = data.frame(timeShortAns = na.omit(data$timeShortAns))

ggplot(dftimeShortAns, aes(x = dftimeShortAns$timeShortAns/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Slide with R Output
```{r showsup, include=FALSE}
#test
summary(cars)
```

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

