---
title: "FYP analyses"
author: "Katie Cheng"
date: "October 8, 2015"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# load libraries
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape)
library(reshape2)

# load functions
source("/Users/Katie/Desktop/Stanford/R/multiplot.R")
source("/Users/Katie/Desktop/Stanford/R/summarySE.R")

# set defaults
options(digits = 3)
```

## Contents

- Histograms of data
- Bar charts comparing group means
- Correlations & scatterplots testing Ease x Utility
- Models for Likelihood, as predicted by Ease & Utility


```{r load_strategy_prompts, include=FALSE}

longStrats = c(
  "Go back and try to figure out something you're confused about in the readings for the class.",
  "Skim new course material to see how it is organized before you study it thoroughly.", 
  "Adjust the way you study in order to fit the course.", 
  "Think through a topic and decide what you are supposed to learn from it before you read it.",
  "Relate ideas you are learning in the course to those in other courses.", 
  "Play around with ideas of your own related to what you are learning in the course.", 
  "Write brief summaries of the main ideas from the readings and the concepts from the lectures.",
  "Set goals for yourself in order to direct your activities in the study period."
)

shortStrats = c(
  "figure_confused",
  "skim_new",
  "adjust_study",
  "decide_learn",
  "relate_courses",
  "play_ideas",
  "summarize_ideas",
  "set_goals"
)

# code strategy dimensions
prepare_act = as.factor(c(1, 0, 0, 0, 1, 1, 1, 0))
open_clearstop = as.factor(c(1, 1, 0, 0, 0, 0, 1, 1))
stratDimensions = data.frame(strategy = c(1:8), 
                             shortStrats,
                             longStrats,
                             prepare_act, 
                             open_clearstop)
stratDimensions$strategy = as.factor(stratDimensions$strategy)
levels(stratDimensions$prepare_act)[1:2] = c("prepare", "act")
levels(stratDimensions$open_clearstop)[1:2] = c("open", "clearstop")
stratDimensions$prepare_act_open_clearstop = paste(stratDimensions$prepare_act, "_", 
                                                   stratDimensions$open_clearstop, sep="")
stratDimensions

```

```{r wrangling, include=FALSE}

# Wrangling raw CSV from Qualtrics

# First, open the CSV and delete the second row (containing descriptive text)
# Why? It messes up the data import

# load data
raw_data = read.csv("/Users/Katie/Desktop/Stanford/1st year project/3_FYP study/version_09-23-15_qualtrics/10-08-15_FYP_Effort_and_Utility_in_SRL2.csv")

# inspect raw data
# dplyr::glimpse(raw_data)

# I don't currently do anything with this
qual_data = dplyr::select(
  raw_data,
  matches("id"),
  matches("ESA1"),
  matches("ESA2"),
  matches("USA1"),
  matches("USA2"),
  matches("C7Time_3"),
  matches("SA1"),
  matches("SA2"),
  matches("^D.")
)

data = dplyr::select(
  raw_data, 
  matches("id"),
  matches("^D."),
  num_range("V", 8:9),
  matches("C3Time_3"),
  matches("ETime_3"),
  matches("UTime_3"),
  matches("LTime_3"),
  matches("C7Time_3"),
  num_range("E", 1:8),
  num_range("U", 1:8),
  num_range("L", 1:8)
)

# Edit survey start & end data:
data = tidyr::separate(data, "V8", c("startDate", "startHour"), sep=" ")
data = tidyr::separate(data, "V9", c("endDate", "endHour"), sep=" ")

# Rename variables
data = dplyr::rename(data, 
                     REP_id = id,
                     timeContext = C3Time_3,
                     timeEase = ETime_3,
                     timeUtility = UTime_3,
                     timeLikelihood = LTime_3,
                     timeShortAns = C7Time_3,
                     age = D1,
                     gender = D2,
                     academicExp = D3,
                     yearMiddle = D3a,
                     yearHigh = D3b,
                     yearCollege = D3c,
                     yearCollegeTxt = D3c_TEXT,
                     yearGrad = D3d,
                     yearGradTxt = D3d_TEXT,
                     taughtStudy = D4
                     )

### fix data ###

# make taughtStudy into ordinal variable
data$taughtStudy = as.ordered(data$taughtStudy)
levels(data$taughtStudy) = c("strongly disagree", "disagree", "sw disagree", 
                             "neither agree nor disagree", "sw agree", 
                             "agree", "strongly agree")

# add a pid
data = cbind("pid" = seq.int(nrow(data)), data)

# turn age from string into an integer
data = tidyr::separate(data, age, c("age", "extra"), sep=2)
data$age = as.integer(data$age)
data$extra = NULL

# make an ageCat variable (note: unevenly distributed bins)
data$ageCat = as.factor(findInterval(data$age, c(16, 21, 26)))
levels(data$ageCat)[1:4] = c("11-15", "16-20", "21-25", "26 & up")

# name levels gender
data$gender = as.factor(data$gender)
levels(data$gender)[1:2] = c("male", "female")

## fix the academic years shenanigans ##

# merge yearCollege and yearCollegeTxt
data$yearCollegeMC = data$yearCollege
data$yearCollege = data$yearCollegeTxt
data$yearCollegeTxt = NULL

# merge yearGrad and yearGradTxt
data$yearGradMC = data$yearGrad
data$yearGrad = data$yearGradTxt
data$yearGradTxt = NULL

# privileging text responses over MC responses
for (i in 1:nrow(data)) {
  if (is.na(data$yearCollege[i])) {
    data$yearCollege[i] = data$yearCollegeMC[i]
  } 
  if (is.na(data$yearGrad[i])) {
    data$yearGrad[i] = data$yearGradMC[i]
  }
}

data$yearCollegeMC = NULL
data$yearGradMC = NULL

# merge all years
# +1 for K, +5 for 1:5, +3 for 6:8, +4 for 9:12, +4 for Frosh-Senior
for (i in 1:nrow(data)) {
  if (is.na(data$academicExp[i])) {
    # do nothing
    data$acadExpYears[i] = data$academicExp[i]
  } else if (data$academicExp[i] == 1) {
    # middle school
    data$acadExpYears[i] = 1 + 5 + data$yearMiddle[i]
  } else if (data$academicExp[i] == 2) {
    # high school
    data$acadExpYears[i] = 1 + 5 + 3 + data$yearHigh[i]
  } else if (data$academicExp[i] == 3) {
    # undergrad
    data$acadExpYears[i] = 1 + 5 + 3 + 4 + data$yearCollege[i]
  } else if (data$academicExp[i] == 4) {
    # grad
    data$acadExpYears[i] = 1 + 5 + 3 + 4 + 4 + data$yearGrad[i]
  }
}

data$yearMiddle = NULL
data$yearHigh = NULL
data$yearCollege = NULL
data$yearGrad = NULL

# name academicExp levels
data$academicExp = as.factor(data$academicExp)
plyr::mapvalues(data$academicExp, from = c(1, 2, 3, 4), 
          to = c("middle", "high", "college", "grad"))

### MELT DATA into long vector###

melt_data = melt(data, id=c(
  "pid", "REP_id", "age", "ageCat", "gender", "academicExp", "acadExpYears", "taughtStudy",
  "startDate", "startHour", "endDate", "endHour", "timeContext", "timeEase", "timeUtility",
  "timeLikelihood", "timeShortAns"))

melt_data = tidyr::separate(melt_data, variable, c("EUL", "strategy"), sep=1)
melt_data$strategy = as.integer(melt_data$strategy)

# fix variable types in melted data
melt_data$taughtStudy = as.ordered(melt_data$taughtStudy)
melt_data$EUL = as.factor(melt_data$EUL)
melt_data$EUL = factor(melt_data$EUL, levels = c("E", "U", "L"))
melt_data$strategy = as.factor(melt_data$strategy)
melt_data = dplyr::rename(melt_data, rating = value)

# add an index
melt_data = cbind("index" = seq.int(nrow(melt_data)), melt_data)

# remove items where the participant didn't rate E, U, and L on the strategy
to_delete = NULL
for (i in 1:nrow(melt_data)) {
  if (is.na(melt_data$rating[i])) {

    participant_id = melt_data$pid[i]
    incomplete_strategy = melt_data$strategy[i]

    delete_rows = as.vector(dplyr::filter(
      melt_data,
      pid==participant_id & strategy==incomplete_strategy)$index)

    to_delete = c(to_delete, delete_rows)
  }
}

melt_data = melt_data[-unique(to_delete), ]

# redo the index now that rows have been deleted
melt_data$index = seq.int(nrow(melt_data))

# add strategy dimensions
melt_data = dplyr::left_join(melt_data, stratDimensions, by="strategy")


### put all ease, all utility, and all likelihood into columns ###

EUL_data = tidyr::gather(data, "item", "rating", 16:39)
EUL_data = tidyr::separate(EUL_data, item, c("EUL", "strategy"), 1)
EUL_data = tidyr::spread(EUL_data, EUL, rating)
EUL_data = data.frame(EUL_data[1:19], EUL_data[21], EUL_data[20])

# rename columns
EUL_data = dplyr::rename(EUL_data, ease = E)
EUL_data = dplyr::rename(EUL_data, utility = U)
EUL_data = dplyr::rename(EUL_data, likelihood = L)

```

```{r make_ordinal}

# can toggle on/off

# data = dplyr::mutate_each_(data, dplyr::funs(as.ordered(.)), names(data[-20:-1]))
# melt_data$rating = as.ordered(melt_data$rating)

```

```{r check_out_data}

dplyr::glimpse(data)
dplyr::glimpse(melt_data)
dplyr::glimpse(EUL_data)

```

Test within-individual EU correlations
--------------------------------------

```{r within_indiv_EU_corr, include=FALSE}

# create a new column in data to store EU correlations
data['indivCorEU'] = NA

for (pid in 1:nrow(data)) {
  eVec = NULL
  uVec = NULL
  for (strat in 1:8) {
    e = data[pid, 15+strat]
    u = data[pid,23+strat]
    
    if (!is.na(e) & !is.na(u)) {
      eVec = c(eVec, e)
      uVec = c(uVec, u)
    }
    if (length(eVec)>2 & length(uVec)>2 &
        sd(eVec)>0 & sd(uVec)>0) {
      corEU = cor.test(eVec, uVec)$estimate
      data$indivCorEU[pid] = corEU
    } 
  }
}

```

### All groups
```{r indivCorEU_all}

summary(data[,'indivCorEU'][!is.na(data$indivCorEU)])
corEU = t.test(data[,'indivCorEU'][!is.na(data$indivCorEU)])

```
To test the null hypothesis that the mean correlation between ease and utility was equal to 0, we conducted t-tests. The result of the t-test shows that the mean `r corEU$estimate` was significantly different from 0 at a p<0.001 level t(`r corEU$parameter`) = `r corEU$statistic`, *p*=`r corEU$p.value`. This means that on average, there was a positive correlation between ease and utility for all participants.


### By `ageCat`
```{r indivCorEU_by_ageCat}

data_split_ageCat = split(data, data$ageCat)

corEU_11_15 = t.test(data_split_ageCat$`11-15`$indivCorEU)
corEU_16_20 = t.test(data_split_ageCat$`16-20`$indivCorEU)
corEU_21_25 = t.test(data_split_ageCat$`21-25`$indivCorEU)
corEU_26_up = t.test(data_split_ageCat$`26 & up`$indivCorEU)

corEU_by_ageCat = aov(indivCorEU ~ ageCat, data = data)
summary(corEU_by_ageCat)
TukeyHSD(corEU_by_ageCat)

```
To test the null hypotheses that the mean correlations were equal to 0, we conducted t-tests. 
The result of the t-test for people of age `11-15` shows that the mean `r corEU_11_15$estimate` was not significantly different from 0 at a p<0.05 level t(`r corEU_11_15$parameter`) = `r corEU_11_15$statistic`, *p*=`r corEU_11_15$p.value`. This means that on average, there was no correlation between ease and utility for `11-15` year olds.

The result of the t-test for people of age `16-20` shows that the mean `r corEU_16_20$estimate` was significantly different from 0 at a p<0.001 level t(`r corEU_16_20$parameter`) = `r corEU_16_20$statistic`, *p*=`r corEU_16_20$p.value`. This means that on average, there was a significant positive correlation between ease and utility for `16-20` year olds.

The result of the t-test for people of age `21-26` shows that the mean `r corEU_21_25$estimate` was significantly different from 0 at a p<0.001 level t(`r corEU_21_25$parameter`) = `r corEU_21_25$statistic`, *p*=`r corEU_21_25$p.value`. This means that on average, there was a significant positive correlation between ease and utility for `21-26` year olds.

The result of the t-test for people of age `26 & up` shows that the mean `r corEU_26_up$estimate` was significantly different from 0 at a p<0.001 level t(`r corEU_26_up$parameter`) = `r corEU_26_up$statistic`, *p*=`r corEU_26_up$p.value`. This means that on average, there was a significant positive correlation between ease and utility for people of age `26 & up`.

To test the relationship between `ageCat` and `indivCorEU`, we fit an analysis of variance model. The model was significant at a *p*<0.05 level, F(`r summary(corEU_by_ageCat)[[1]][["Df"]][1]`) = `r summary(corEU_by_ageCat)[[1]][["F value"]][1]`, *p*=`r summary(corEU_by_ageCat)[[1]][["Pr(>F)"]][1]`. In other words, there is a significant relationship between age-category and mean correlation between ease and utility.

To test whether there were significant differences between pairs of groups, we conducted a  Tukey Honest Significant Differences test. There was a marginally significant difference in correlations diff=`r TukeyHSD(corEU_by_ageCat)[[1]][[2,1]]` between `21-25` and `11-15` year olds at a p<0.05 level, *p*=`r TukeyHSD(corEU_by_ageCat)[[1]][[2,4]]`, but no significant differences between any other pairs of age-categories. 

### By `academicExp` (middle vs. high vs. college vs. grad)
```{r indivCorEU_by_academicExp}

data_split_academicExp = split(data, data$academicExp)

# currently have no middle schoolers
# corEU_middle = t.test(data_split_academicExp$`1`$indivCorEU)

corEU_high = t.test(data_split_academicExp$`2`$indivCorEU)
corEU_college = t.test(data_split_academicExp$`3`$indivCorEU)
corEU_grad = t.test(data_split_academicExp$`4`$indivCorEU)

corEU_by_academicExp = aov(indivCorEU ~ academicExp, data = data)
summary(corEU_by_academicExp)
TukeyHSD(corEU_by_academicExp)

```
**ADD INTERPRETATION LATER**

### Same thing without strategy #1
```{r within_indiv_EU_corr_wo1, include=FALSE}

# create a new column in data to store EU correlations
data['indivCorEUwo1'] = NA

for (pid in 1:nrow(data)) {
  eVec = NULL
  uVec = NULL
  for (strat in 2:8) {
    e = data[pid, 15+strat]
    u = data[pid,23+strat]
    
    if (!is.na(e) & !is.na(u)) {
      eVec = c(eVec, e)
      uVec = c(uVec, u)
    }
    if (length(eVec)>2 & length(uVec)>2 &
        sd(eVec)>0 & sd(uVec)>0) {
      corEU = cor.test(eVec, uVec)$estimate
      data$indivCorEUwo1[pid] = corEU
    } 
  }
}

# all 
summary(data[,'indivCorEUwo1'][!is.na(data$indivCorEUwo1)])
corEUwo1 = t.test(data[,'indivCorEUwo1'][!is.na(data$indivCorEUwo1)])

# by ageCat
data_split_ageCat = split(data, data$ageCat)

corEU_11_15_wo1 = t.test(data_split_ageCat$`11-15`$indivCorEUwo1)
corEU_16_20_wo1 = t.test(data_split_ageCat$`16-20`$indivCorEUwo1)
corEU_21_25_wo1 = t.test(data_split_ageCat$`21-25`$indivCorEUwo1)
corEU_26_up_wo1 = t.test(data_split_ageCat$`26 & up`$indivCorEUwo1)

corEU_by_ageCat_wo1 = aov(indivCorEUwo1 ~ ageCat, data = data)
summary(corEU_by_ageCat_wo1)
TukeyHSD(corEU_by_ageCat_wo1)

# by academicExp
data_split_academicExp = split(data, data$academicExp)

corEU_high_wo1 = t.test(data_split_academicExp$`2`$indivCorEUwo1)
corEU_college_wo1 = t.test(data_split_academicExp$`3`$indivCorEUwo1)
corEU_grad_wo1 = t.test(data_split_academicExp$`4`$indivCorEUwo1)

corEU_by_academicExp_wo1 = aov(indivCorEUwo1 ~ academicExp, data = data)
summary(corEU_by_academicExp_wo1)
TukeyHSD(corEU_by_academicExp_wo1)

```

## Plot strategies, colored by open_clstop, by `ageCat`
```{r plot_strats_colorOC_by_ageCat, fig.width=10, fig.height=10}

summary_PO = summarySE(melt_data, measurevar="rating", groupvars=c('strategy', 'EUL', 'prepare_act', 'open_clearstop', 'ageCat'))

#11-15
filter_ease = dplyr::filter(summary_PO, EUL=="E" & ageCat=="11-15")
filter_utility = dplyr::filter(summary_PO, EUL=="U" & ageCat=="11-15")

ggplot(dplyr::filter(summary_PO, ageCat=="11-15"), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "age 11-15")

# 16-20
filter_ease = dplyr::filter(summary_PO, EUL=="E" & ageCat=="16-20")
filter_utility = dplyr::filter(summary_PO, EUL=="U" & ageCat=="16-20")

ggplot(dplyr::filter(summary_PO, ageCat=="16-20"), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "age 16-20")

# 21-25
filter_ease = dplyr::filter(summary_PO, EUL=="E" & ageCat=="21-25")
filter_utility = dplyr::filter(summary_PO, EUL=="U" & ageCat=="21-25")

ggplot(dplyr::filter(summary_PO, ageCat=="21-25"), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "age 21-25")

# 26 & up
filter_ease = dplyr::filter(summary_PO, EUL=="E" & ageCat=="26 & up")
filter_utility = dplyr::filter(summary_PO, EUL=="U" & ageCat=="26 & up")

ggplot(dplyr::filter(summary_PO, ageCat=="26 & up"), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "age 26 & up")

```

## Plot strategies, colored by open_clstop, by `academicExp`
```{r plot_strats_colorOC_by_ageCat, fig.width=10, fig.height=10}

summary_PO = summarySE(melt_data, measurevar="rating", groupvars=c('strategy', 'EUL', 'prepare_act', 'open_clearstop', 'academicExp'))

# high
filter_ease = dplyr::filter(summary_PO, EUL=="E" & academicExp==2)
filter_utility = dplyr::filter(summary_PO, EUL=="U" & academicExp==2)

ggplot(dplyr::filter(summary_PO, academicExp==2), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "high school")

# college
filter_ease = dplyr::filter(summary_PO, EUL=="E" & academicExp==3)
filter_utility = dplyr::filter(summary_PO, EUL=="U" & academicExp==3)

ggplot(dplyr::filter(summary_PO, academicExp==3), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "college")

# grad
filter_ease = dplyr::filter(summary_PO, EUL=="E" & academicExp==4)
filter_utility = dplyr::filter(summary_PO, EUL=="U" & academicExp==4)

ggplot(dplyr::filter(summary_PO, academicExp==4), aes(x=filter_ease$rating, 
                       y=filter_utility$rating, colour=filter_ease$open_clearstop)) +
  geom_point() +
  geom_errorbar(aes(ymin = filter_utility$rating - filter_utility$ci, 
                    ymax = filter_utility$rating + filter_utility$ci)) +
  geom_errorbarh(aes(xmin = filter_ease$rating - filter_ease$ci, 
                     xmax = filter_ease$rating + filter_ease$ci)) +
  geom_text(aes(label=filter_ease$strategy, hjust=1.5, vjust=1.5)) + 
  labs(title = "grad school")

```


```{r lme_model_EUL}
# Number of Observations: 1056

# predicting likelihood with scaled ease
ease_model = nlme::lme(likelihood ~ scale(ease), 
                       random = ~1 | pid, 
                       data = dplyr::filter(EUL_data, !is.na(likelihood)))
summary(ease_model)

# predicting likelihood with scaled utility
utility_model = nlme::lme(likelihood ~ scale(utility), 
                          random = ~1 | pid, 
                          data = dplyr::filter(EUL_data, !is.na(likelihood)))
summary(utility_model)

# predicting likelihood with scaled ease & utility
add_model = nlme::lme(likelihood ~ scale(ease) + scale(utility), 
                      random = ~1 | pid, 
                      data = dplyr::filter(EUL_data, !is.na(likelihood)))
summary(add_model)

# predicting likelihood with the interaction of scaled ease & utility
interact_model = nlme::lme(likelihood ~ scale(ease) * scale(utility), 
                           random = ~1 | pid, 
                           data = dplyr::filter(EUL_data, !is.na(likelihood)))
summary(interact_model)

# anova to compare models
anova(ease_model, utility_model, add_model, interact_model)

```

```{r lme_model_EUL_age}

# repeat of prior codeblock, this time with age in the model (which changes the max number of observations we can use in the model)

# Number of Observations: 1040

ease_model2 = nlme::lme(likelihood ~ scale(ease), 
                       random = ~1 | pid, 
                       data = dplyr::filter(EUL_data, !is.na(age)))

utility_model2 = nlme::lme(likelihood ~ scale(utility), 
                          random = ~1 | pid, 
                          data = dplyr::filter(EUL_data, !is.na(age)))

add_model2 = nlme::lme(likelihood ~ scale(ease) + scale(utility), 
                      random = ~1 | pid, 
                      data = dplyr::filter(EUL_data, !is.na(age)))

interact_model2 = nlme::lme(likelihood ~ scale(ease) * scale(utility), 
                           random = ~1 | pid, 
                           data = dplyr::filter(EUL_data, !is.na(age)))

interact_age_model = nlme::lme(likelihood ~ scale(ease) * scale(utility) + age, 
                           random = ~1 | pid, 
                           data = dplyr::filter(EUL_data, !is.na(age)))
summary(interact_age_model)

# anova to compare models
anova(ease_model2, utility_model2, add_model2, interact_model2, interact_age_model)

```

```{r lme_model_EUL_acadExpYears}

# repeat of prior codeblock, this time with academic experience in years in the model (which changes the max number of observations we can use in the model)

# less significant than age

# Number of Observations: 1016
# Number of Groups: 127 (participants)

filtered_data = dplyr::filter(dplyr::filter(EUL_data, !is.na(academicExp)),
                              !is.na(acadExpYears))

ease_model3 = nlme::lme(likelihood ~ scale(ease), 
                       random = ~1 | pid, 
                       data = filtered_data)

utility_model3 = nlme::lme(likelihood ~ scale(utility), 
                          random = ~1 | pid, 
                          data = filtered_data)

add_model3 = nlme::lme(likelihood ~ scale(ease) + scale(utility), 
                      random = ~1 | pid, 
                      data = filtered_data)

interact_model3 = nlme::lme(likelihood ~ scale(ease) * scale(utility), 
                           random = ~1 | pid, 
                           data = filtered_data)

interact_acadExpYears_model = nlme::lme(likelihood ~ scale(ease) * scale(utility) + acadExpYears, 
                           random = ~1 | pid, 
                           data = filtered_data)
summary(interact_acadExpYears_model)

# anova to compare models
anova(ease_model3, utility_model3, add_model3, interact_model3, interact_acadExpYears_model)

```









## "I study the way that I do because a teacher (or teachers) taught me to study that way."

```{r hist_taughtStudy, fig.width=10, fig.height=6}

dfTaught = data.frame(taughtStudy = na.omit(data$taughtStudy))

ggplot(dfTaught, aes(x = taughtStudy)) +
  geom_histogram(color='black',
                 fill='lightgrey',
                 binwidth=1,
                 breaks=c(0.5:7.5)) +
  theme_bw()

```


## Time on task: Reading context
```{r hist_time_context, fig.width=10, fig.height=6}

dftimeContext = data.frame(timeContext = na.omit(data$timeContext))

ggplot(dftimeContext, aes(x = dftimeContext$timeContext)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("milliseconds") +
  theme_bw()

```

## Time on task: Doing Ease likert rating & short answers
```{r hist_time_ease, fig.width=10, fig.height=6}

dftimeEase = data.frame(timeEase = na.omit(data$timeEase))

ggplot(dftimeEase, aes(x = dftimeEase$timeEase/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Time on task: Doing Utility likert rating & short answers
```{r hist_time_utility, fig.width=10, fig.height=6}

dftimeUtility = data.frame(timeUtility = na.omit(data$timeUtility))

ggplot(dftimeUtility, aes(x = dftimeUtility$timeUtility/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Time on task: Doing Likelihood likert rating
```{r hist_time_likelihood, fig.width=10, fig.height=6}

dftimeLikelihood = data.frame(timeLikelihood = na.omit(data$timeLikelihood))

ggplot(dftimeLikelihood, aes(x = dftimeLikelihood$timeLikelihood/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Time on task: Doing short answer descriptions of study strategies
```{r hist_time_sa, fig.width=10, fig.height=6}

dftimeShortAns = data.frame(timeShortAns = na.omit(data$timeShortAns))

ggplot(dftimeShortAns, aes(x = dftimeShortAns$timeShortAns/100)) +
  geom_histogram(aes(y=..density..), # ..density.. normalizes the y axis to counts/total
                 color='darkgrey',
                 fill='lightgrey',
                 binwidth=1) +
                 # breaks=c(0.5:7.5)) + 
  geom_density(alpha=0.2,
               fill='lightgrey',
               adjust=3) +
  xlab("seconds") +
  theme_bw()

```

## Slide with R Output
```{r showsup, include=FALSE}
#test
summary(cars)
```

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

